WSClean: an implementation of a fast, generic wide-field imager

### 2014-03-14 articles/2014/Article-WSClean/wsclean.tex
Replacing fullsky image with better axes
Spelling error

\begin{figure*}
\begin{center}
\includegraphics[width=13.5cm]{img/fullsky-together}
\caption{A beam-corrected MWA image of a 112~s zenith observation at 180~MHz that covers almost the full sky. The lower image shows a zoom-in on the southern side lobe. PKS J2358-6054 ($\sim100$ Jy) is visible in the centre of the southern side lobe and resolved. The noise level in the side lobe is about 200 mJy. PKS J2358-6054 has been cleaned, but some artefacts remain because no direction-dependent calibration has been performed.}
\label{fig:full-sky-example}
\end{center}
\end{figure*}

@@

An example of the difference in projection between non-recentred and recentred imaging is given in Fig.~\ref{fig:vela-projection-example}, which displays a 13-min MWA observation imaged with \textsc{wsclean}. The processing steps performed for this image were: i) preprocessing of the observation with the Cotter preprocessing pipeline, which include time averaging and RFI flagging with the \textsc{aoflagger} \citep{post-correlation-rfi-classification,scale-invariant-rank-operator}; ii) calibration using Hydra~A without direction dependence using a custom implementation of the RTS full-polarization calibration algorithm \citep{rts-mwa}; and iii) imaging of the seven 112 s intervals separately. Cleaning an image that is in a different projection yields slightly different results, but qualitatively the two images are clearly of equal accuracy. The wall-clock time for imaging is 60 min and 41 min for normal projection and the recentred image, respectively. Of the 41 min, 3 min is spent on phase rotating the visibilities.

>>>>

\begin{figure*}
\begin{center}
\includegraphics[height=22.5cm]{img/fullsky-together}
\caption{A beam-corrected MWA image of a 112~s zenith observation at 180~MHz that covers almost the full sky. The lower image shows a zoom-in on the southern side lobe. PKS J2358-6054 ($\sim100$ Jy) is visible in the centre of the southern side lobe and resolved. The noise level in the side lobe is about 200 mJy. PKS J2358-6054 has been cleaned, but some artefacts remain because no direction-dependent calibration has been performed.}
\label{fig:full-sky-example}
\end{center}
\end{figure*}

@@

An example of the difference in projection between non-recentred and recentred imaging is given in Fig.~\ref{fig:vela-projection-example}, which displays a 13-min MWA observation imaged with \textsc{wsclean}. The processing steps performed for this image were: i) preprocessing of the observation with the Cotter preprocessing pipeline, which includes time averaging and RFI flagging with the \textsc{aoflagger} \citep{post-correlation-rfi-classification,scale-invariant-rank-operator}; ii) calibration using Hydra~A without direction dependence using a custom implementation of the RTS full-polarization calibration algorithm \citep{rts-mwa}; and iii) imaging of the seven 112 s intervals separately. Cleaning an image that is in a different projection yields slightly different results, but qualitatively the two images are clearly of equal accuracy. The wall-clock time for imaging is 60 min and 41 min for normal projection and the recentred image, respectively. Of the 41 min, 3 min is spent on phase rotating the visibilities.
